\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage[british]{babel}

\usepackage[today]{svninfo}
\svnInfo $Id: devise.tex 0 2015-03-20 21:43:38Z michaelstokes $

\usepackage{url}

\title{Devise- Uni-Sale}
\author{Michael A Stokes, \texttt{Michael Stokes}}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
Implementing Devise within the website for User
privilidges such as login, register etc.

\subsection{Installation}

\begin{enumerate}
\item gem devise
\item rails generate devise:install
\item rails generate devise:views
\item rails generate devise User
\item rake db:migrate
\item rails server
\end{enumerate}

\subsection{Devise Configurations}

\subsubsection{Modules}
Extra Modules will be added:

\begin{enumerate}
\item Confirmable : sends emails with confirmation instructions and verifies whether an account is already confirmed during sign in
{\url{http://www.rubydoc.info/github/plataformatec/devise/master/Devise/Models/Confirmable}}
\item Timeoutable : expires sessions that have not been active in a specified period of time.
{\url{http://www.rubydoc.info/github/plataformatec/devise/master/Devise/Models/Timeoutable}}
\item Lockable : locks an account after a specified number of failed sign-in attempts. Can unlock via email or after a specified time period.
{\url{http://www.rubydoc.info/github/plataformatec/devise/master/Devise/Models/Lockable}}
\end{enumerate}

\subsubsection{User Attributes}
Extra Attributes will be added to the User and Devise Configuration:
\begin{enumerate}

	\item Username : Users must register a username and will be able to login by that username. The 	username is the Users identity.
		\begin{enumerate}
			\item rails generate migration add\_username\_to\_users username:string:uniq
			\item before\_action :configure\_permitted\_parameters, if: :devise\_controller?
			\item attr\_accessor :login
			\hfill \\
			{\url{https://github.com/plataformatec/devise/wiki/How-To:-Allow-users-to-sign-in-using-		their-username-or-email-address}}
		\end{enumerate}

	\item First Name : Users must register a First Name.
		\begin{enumerate}
			\item rails generate migration add\_first\_name\_to\_users first\_name:string
		\end{enumerate}

	\item Last Name : Users must register a Last Name.
		\begin{enumerate}
			\item rails generate migration add\_last\_name\_to\_users last\_name:string
		\end{enumerate}

	\item Phone Number : Users must register a Phone Number.
		\begin{enumerate}
			\item rails generate migration add\_phone\_number\_to\_users phone\_number:string
		\end{enumerate}

		\item All : Username, First Name, Last Name, Phone Number
			\begin{enumerate}
				\item rails generate migration add\_extra\_attributes\_to\_users phone\_number:string first\_name:string last\_name\_string
			\end{enumerate}

	\item rake db:migrate
\end{enumerate}

\subsubsection{User Attributes}
Extra Attributes will be added to the User and Devise Configuration:
\begin{enumerate}

\item Groups : Users belong to 1 or many groups.
	A user can belong to many groups, a user may be general internal user or external user i.e. student or company.
	If a student then normal site, if company then different panel.

	User Groups
	\begin{enumerate}
		\item id - The id.
		\item user\_id - The id of the user.
		\item group\_id - The id of the group the user belongs to.
		\item rails generate model User\_Groups user\_id:integer group\_id:integer
	\end{enumerate}


Groups
\begin{enumerate}
	\item id - The id.
	\item name - The name of the group.
	\item description - The description of the group.
	\item rails g model Groups name:String description:Text
\end{enumerate}

\end{enumerate}

	\item Username : Users must register a username and will be able to login by that username. The 	username is the Users identity.
		\begin{enumerate}
			\item rails generate migration add\_username\_to\_users username:string:uniq
			\item before\_action :configure\_permitted\_parameters, if: :devise\_controller?
			\item attr\_accessor :login
			\hfill \\
			{\url{https://github.com/plataformatec/devise/wiki/How-To:-Allow-users-to-sign-in-using-		their-username-or-email-address}}
		\end{enumerate}

\subsubsection{Override Default Devise}
We will override the default Devise Configuration and thus generate a Devise Controller and then override the methods i.e. in registration and session.

\begin{enumerate}
	\item Controller : Override default Devise and generate Devise Controllers:
		\begin{enumerate}
			\item rails generate devise:controllers users
			\item Add Filters i.e. before calling create call private method prior\_create to check domain valid and other checks etc and if not redirect with flash message.
			\hfill \\
			{\url{https://github.com/plataformatec/devise}}
		\end{enumerate}
	\item Routes : Alter the Routes to use the defined Devise Controllers:
	\begin{enumerate}
		\item Registrations and Sessions Controller for Sign\_up and Login
	\end{enumerate}
			\hfill \\
			{\url{https://github.com/plataformatec/devise}}
\end{enumerate}

\section{Registration}
Implementing Devise Custom Registration. The default Devise Configuration will be changed and thus Devise Controller Actions will be override and filters will be used.

\subsection{Registration Steps}

\begin{enumerate}
\item User Enters Registration details
\item Controller called, before filter in place i.e. before create in register controller is called prior\_create will be called rather which will perform many checks.
\item Registration prior create checks include:
	\begin{enumerate}
		\item Validation.
		\item Check Domain, is it a valid ac.uk address i.e. surrey.ac.uk and does it exist in the Domains table.
		\item Uniqueness.
	\end{enumerate}
\item Registration Post Steps include:
	\begin{enumerate}
		\item Send Activation Email
		\item User Activates and then can login.
	\end{enumerate}
\end{enumerate}

\subsubsection{Confirmable}
The Extra Module Confirmable to be added:
\begin{enumerate}
			\item devise :registerable, :confirmable
			\item rails g migration add_confirmable_to_devise
			\item Change migration file.
			\hfill \\
			{\url{https://github.com/plataformatec/devise/wiki/How-To:-Add-:confirmable-to-Users}}
		\end{enumerate}

\begin{thebibliography}{9}

\bibitem{devise}
  Devise - Ruby Gem
  \emph{: User Login/Register}.
  {\url{https://github.com/plataformatec/devise}},
\end{thebibliography}



\end{document}
