\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage[british]{babel}

\usepackage[today]{svninfo}
\svnInfo $Id: contribution_michaelstokes.tex 0 2015-03-20 10:04:38Z michaelstokes $

\title{Weekly Contributions to Uni-Sale}
\author{Michael A Stokes, \texttt{michael stokes}}
\date{\today}

\begin{document}

\maketitle

\section{Week 01}
In Week 01, I begun the creation of the Ruby on Rails Uni-Sale Website.
Firstly I set up the bitbucket git repository, I then introduced a code and documentation folder.
The code folder includes the rails project whilst the documentation folder includes documentation including design, contributions, tasks etc.

For documentation I begun creating tasks files i.e. activeadmin, devise to provide a review of the steps taken in the installations and configurations.
I also included an initial UML Diagram.

This initial creation included creating the core controller i.e. for the index, about us and legal pages.
I then went on to install, create and configure the Devise Gem for user login/registration and activeadmin Gem 
for administrative privileges i.e. manipulating users, items, etc.
I set up the default views, but design is not a priority.
I also added activeadmin resource for model User i.e. for the manipulation of user(s) and this includes adding, modifying and removing users.

\begin{enumerate}
\item Created Initial Project for Ruby on Rails Uni-Sale Website.
\item Create Documentation folder for all documentation.
\item Created Task Files i.e. for devise and activeadmin installations and configurations.
\item Generated Core Controller.
\item Installed and Configured Devise Gem for login/registration.
\item Installed and Configured activeadmin Gem for administrative privileges.
\item Added activeadmin resource model User.
\end{enumerate}

\section{Week 02}
...

\end{document}
